\documentclass{report}
    \usepackage[utf8]{inputenc}
    \usepackage{graphicx}
    \graphicspath{{./resources/images}}
    \usepackage{sectsty} 
    \usepackage[dvipsnames]{xcolor}
    \definecolor{MyMidBlack}{HTML}{232b2b}
    \definecolor{MyGold}{HTML}{F7B733}
    \definecolor{MyLinkBlue}{HTML}{00B0FF}
    \sectionfont{\color{MyGold}}
    
    
    \title{%
      Sponsorship Prospectus \\
      \large University of Liverpool Hackathon Society}
    \author{HackSoc Committee}
    \date{March NA/NA/2018}
    
    \begin{document}


    \pagecolor{MyMidBlack}
    \color{white}
    
    \maketitle
    
    \section *{Introduction}
    We are University Of Liverpool Hackathon Society (or HackSoc). A Hackathon is an event where many team build cool things... Our Vision is to bring talented developers, designer, entrepreneur and more to Liverpool. We want Liverpool to be recognised as a great Tech spot. Similar to other city such as Manchester, Notttingham, Surrey and more...
    
    
    \section *{Why Should You Sponsor Us?}
    
    \begin{itemize}
        \item[$\bullet$] \textbf{Attract talented and driven students: }You will attract passionate students
        who can work as part of a team and under pressure to bring our the best they can offer.
        \item[$\bullet$] \textbf{You can advertise your latest tech: }If you have a new API, this is the 
        best way to challenge these students and let their imagination bring out the possibility of your latest
        tech.
        \item[$\bullet$] \textbf{Send your technical staff: }You can send your developers to find suitable 
        students to work for you. This is a great opportunity to hire students, as you can see them in action, 
        rather than looking up them up on a CV.
    
    \end{itemize}
     
    
      
    
    \section *{Get in Touch}
    If you are interested or would like to discuss additional details ]. You can contact us via email: \textcolor{MyLinkBlue}{LivHackSoc@email.com}. Additionally, you
    can contact our Committee Hackathon Organiser Brandon Skerrit on \textcolor{MyLinkBlue}{+44 1234 567891}

    \section *{Sponsorship Tiers}
    What you can offer and what will you can gain from sponsoring us.
    
    \end{document}
    